Proposal for Analyzing Language Models: Separatablity of Syntax and Semantics

### 2022-04-27 proposal/proposal.tex
adding citation

To evaluate the separability of syntax and semantics, we will need two task, one task for the probing system and INLP procedure, one task for measure performance on embeddings before and after INLP. We choose Combinatory Categorical Grammar (CCG) tagging as the syntactic task and Semantic Role Labeling (SRL) as the semantic task. Section \ref{sec:method} provides description of the tasks and the construction of the experiment pipeline. Section \ref{sec:result} provddes possible results and interpretations. Finally, section \ref{sec:management} provides project management details including timeline and division of labor.
% If the removing of syntactic information leads to a insignificant decrease in the model\rq s performance in a semantic task (or removing semantic information leads to insignificant decrease in performance in a syntactic task), we can conclude that syntactic and semantic information in BERT\rq s representation is linearly separable. Conversely, an significant decrease in performance will indicate low separability between syntactic and semantic information in BERT \rq s representation.

@@

%Description of the data set used and the information it contains relevant to the tasks of interest. Talk about pre-processing the syntax trees to get CCG tags. 
We will use the English V4 subset of the CoNLL 2012 shared task data. We must perform two pre-processing steps for this data to be used for our probing and evaluation tasks. The first is to apply Hockenmaier and Steedman's CCG Derivation algorithm to the parse tree field in the dataset, in order to create the CCG tags for each word. If this proves to be too time-consuming or computationally expensive then we shall change the syntactic probing task to utilize the POS tags available in the dataset, in place of CCG tags. The second task is to use the SRL frames in the dataset to generate (verb, BIO-argument-tag) pairs that will act as the categories for the semantic probing task. 
%cite CCG paper

@@

\section{Divsion of Labor and Timeline}
\label{sec:management}
this is

>>>>

To evaluate the separability of syntax and semantics, we will need two task, one task for the probing system and INLP procedure, one task for evaluating performance on embeddings before and after INLP. We choose Combinatory Categorical Grammar (CCG) tagging as the syntactic task and Semantic Role Labeling (SRL) as the semantic task. Section \ref{sec:method} provides description of the tasks and the construction of the experiment pipeline. Section \ref{sec:result} provides possible results and interpretations. Finally, section \ref{sec:management} provides project management details including timeline and division of labor.

@@

%Description of the data set used and the information it contains relevant to the tasks of interest. Talk about pre-processing the syntax trees to get CCG tags. 
We will use the English V4 subset of the CoNLL 2012 shared task data\citep{2012-conll} . We must perform two pre-processing steps for this data to be used for our probing and evaluation tasks. The first is to apply \citet{ccg-bank}'s CCG Derivation algorithm to the parse tree field in the dataset, in order to create the CCG tags for each word. If this proves to be too time-consuming or computationally expensive then we shall change the syntactic probing task to utilize the POS tags available in the dataset, in place of CCG tags. The second task is to use the SRL frames in the dataset to generate (verb, BIO-argument-tag) pairs that will act as the categories for the semantic probing task. 
%cite CCG paper

@@

% If the removing of syntactic information leads to a insignificant decrease in the model\rq s performance in a semantic task (or removing semantic information leads to insignificant decrease in performance in a syntactic task), we can conclude that syntactic and semantic information in BERT\rq s representation is linearly separable. Conversely, an significant decrease in performance will indicate low separability between syntactic and semantic information in BERT \rq s representation.

\section{Divsion of Labor and Timeline}
\label{sec:management}
There are three main parts of this project, coding the experiment, presenting related topics in class and writing the final paper. Each part has detailed roles and
